### 2023-01-05 ms.rmd
JUst supressing some code and messages in code chunks for rendering

A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers. `r utils::packageVersion("rotl")`, ]. Branch lengths were computed using Gafen's method []

@@

```{r, wildlnRR10}
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

@@

```{r wildlncvr}
#######################################
  ## lnCVRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

>>>>

A phylogenetic tree was created using the Open Tree of Life (OTL) with the *rotl* package in R [vers. `r utils::packageVersion("rotl")`, ]. We resolved all polytomies in the tree and replaced any missing taxa with closely related species. Branch lengths were computed using Gafen's method []

@@

```{r, wildlnRR10, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

@@

```{r wildlncvr, echo = FALSE, message=FALSE, warning=FALSE, results='hide'}
#######################################
  ## lnCVRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################
